Gafo-cc visuals

### 2024-03-15 analysis/gafo-cc-visuals.Rmd
add missing site descriptions to supplement

ggplot(sim_dat, aes(x = targetposition, y= mean, col = col))+
  background_image(im2) + 
  geom_point(size = 3)+
  geom_jitter(aes(y = impr), alpha = 0.1, width = 0.1)+
  scale_color_manual(values = c("black", "firebrick"), guide = "none")+
  ylim(0, 1000)+
  labs(x = "Target position (binned)", y = "Imprecision")+
  theme_few()

@@

ggplot(sim_dat2, aes(x = targetposition, y= mean, col = col))+
  background_image(im4) + 
  geom_point(size = 3)+
  geom_jitter(aes(y = impr), alpha = 0.1, width = 0.1)+
  scale_color_manual(values = c("black", "firebrick"), guide = "none")+
  ylim(0, 1000)+
  labs(x = "Target position (binned)", y = "Imprecision")+
  theme_few()

>>>>

ggplot(sim_dat, aes(x = targetposition, y= mean, col = col))+
  background_image(im2) + 
  geom_point(size = 3)+
  geom_jitter(aes(y = impr), alpha = 0.1, width = 0.1)+
  scale_color_manual(values = c("black", "firebrick"), guide = "none")+
  ylim(0, 1000)+
  labs(x = "Target position (binned)", y = "Imprecision (simulated)")+
  theme_few()

@@

ggplot(sim_dat2, aes(x = targetposition, y= mean, col = col))+
  background_image(im4) + 
  geom_point(size = 3)+
  geom_jitter(aes(y = impr), alpha = 0.1, width = 0.1)+
  scale_color_manual(values = c("black", "firebrick"), guide = "none")+
  ylim(0, 1000)+
  labs(x = "Target position (binned)", y = "Imprecision (simulated)")+
  theme_few()
